### 2018-03-19 submission/manuscript.Rmd
update bray-curtis results section

***Minimal Bray-Curtis Differences are Detected by Cycle Number:***
A few small differences based on sub-sampling and cycle number were detected in bacterial communities. Within the same fecal sample and independent of HiFi DNA polymerases, there were differences in the community composition between 20 and 25 cycles that was dependent on sub-sampling depth (sub-sampled to 1000 = `r round(median(filter(dist_data[["1000"]], cycle_compare == "20to25")[, "distance"]), digits = 2)` (`r round(quantile(filter(dist_data[["1000"]], cycle_compare == "20to25")[, "distance"])["25%"], digits = 2)` - `r round(quantile(filter(dist_data[["1000"]], cycle_compare == "20to25")[, "distance"])["75%"], digits = 2)`) (median (25% - 75% quantile)), sub-sampled to 5000 = `r round(median(filter(dist_data[["5000"]], cycle_compare == "20to25")[, "distance"]), digits = 2)` (`r round(quantile(filter(dist_data[["5000"]], cycle_compare == "20to25")[, "distance"])["25%"], digits = 2)` - `r round(quantile(filter(dist_data[["5000"]], cycle_compare == "20to25")[, "distance"])["75%"], digits = 2)`), sub-sampled to 10000 = `r round(median(filter(dist_data[["10000"]], cycle_compare == "20to25")[, "distance"]), digits = 2)` (`r round(quantile(filter(dist_data[["10000"]], cycle_compare == "20to25")[, "distance"])["25%"], digits = 2)` - `r round(quantile(filter(dist_data[["10000"]], cycle_compare == "20to25")[, "distance"])["75%"], digits = 2)`)) [Figure 3A]. Further, where data was available for the mock communities, there were larger observed differences between 20 and 25 cycles (sub-sampled to 1000 = `r round(median(filter(mock_dist_data[["1000"]], cycle_compare == "20to25")[, "distance"]), digits = 2)` (`r round(quantile(filter(mock_dist_data[["1000"]], cycle_compare == "20to25")[, "distance"])["25%"], digits = 2)` - `r round(quantile(filter(mock_dist_data[["1000"]], cycle_compare == "20to25")[, "distance"])["75%"], digits = 2)`)) [Figure 3B]. Additionally, these stated community differences disappear when comparing 25 to 30 cycles and do not persist past 25 cycles [Figure 3]. Finally, using PERMANOVA to test for community differences based on cycle number within HiFi DNA polymerases, only Phusion had cycle dependent differences at 1000 and 5000 sub-sampling depths (P-value = `r format(filter(bray_permanova_by_taq_results, sub_sample_level == 1000, taq == "PHU")[, "bh"], digits = 1, nsmall = 1)` and `r format(filter(bray_permanova_by_taq_results, sub_sample_level == 5000, taq == "PHU")[, "bh"], digits = 1, nsmall = 1)`, respectively). Phusion was one of two HiFi DNA polymerases that had enough sequences to reach a sub-sampling depth of 1000 at 15 cycles for fecal samples.

Next, we assessed whether there were any differences between 5-cycle increments within each individual or sample replicate. For both fecal and mock samples, we found that there was no detectable difference in Bray-Curtis index when comparing to the previous 5-cycle increment (P-value `r ifelse(min(bray_sim_to_prev_cycle_kruskal_results$bh, na.rm = T) > 0.05, invisible(">"), invisible("check data"))` 0.05). However, Phusion at 1000 sub-sampling depth had a P-value = `r format(filter(bray_sim_to_prev_cycle_kruskal_results, sub_sample_level == 1000, taq == "PHU")[, "pvalue"], digits = 1, nsmall = 1)` before multiple comparison correction. Similar to the PERMANOVA analysis, at higher sub-sampling depths these differences in Bray-Curtis indices disappear. Overall, HiFi DNA polymerase differences in Bray-Curtis index are dependent on both sub-sampling depth and cycle number.

>>>>

***Minimal Bray-Curtis Differences are Detected by Cycle Number:***
A few small differences based on sub-sampling and cycle number were detected in overall bacterial community composition. Within the same fecal sample and independent of HiFi DNA polymerases, there were differences in the community composition between 20 and 25 cycles that was dependent on sub-sampling depth (sub-sampled to 1000 = `r round(median(filter(dist_data[["1000"]], cycle_compare == "20to25")[, "distance"]), digits = 2)` (`r round(quantile(filter(dist_data[["1000"]], cycle_compare == "20to25")[, "distance"])["25%"], digits = 2)` - `r round(quantile(filter(dist_data[["1000"]], cycle_compare == "20to25")[, "distance"])["75%"], digits = 2)`) (median (IQR)), sub-sampled to 5000 = `r round(median(filter(dist_data[["5000"]], cycle_compare == "20to25")[, "distance"]), digits = 2)` (`r round(quantile(filter(dist_data[["5000"]], cycle_compare == "20to25")[, "distance"])["25%"], digits = 2)` - `r round(quantile(filter(dist_data[["5000"]], cycle_compare == "20to25")[, "distance"])["75%"], digits = 2)`), sub-sampled to 10000 = `r round(median(filter(dist_data[["10000"]], cycle_compare == "20to25")[, "distance"]), digits = 2)` (`r round(quantile(filter(dist_data[["10000"]], cycle_compare == "20to25")[, "distance"])["25%"], digits = 2)` - `r round(quantile(filter(dist_data[["10000"]], cycle_compare == "20to25")[, "distance"])["75%"], digits = 2)`)) [Figure 3A]. Further, when data was available for the mock communities, there were larger observed differences between 20 and 25 cycles (sub-sampled to 1000 = `r round(median(filter(mock_dist_data[["1000"]], cycle_compare == "20to25")[, "distance"]), digits = 2)` (`r round(quantile(filter(mock_dist_data[["1000"]], cycle_compare == "20to25")[, "distance"])["25%"], digits = 2)` - `r round(quantile(filter(mock_dist_data[["1000"]], cycle_compare == "20to25")[, "distance"])["75%"], digits = 2)`)) [Figure 3B]. Additionally, these stated community differences disappear when comparing 25 to 30 cycles and do not persist past 25 cycles [Figure 3]. Although these trends are clearly noticeable, we found that there was no detectable difference in Bray-Curtis index when comparing to the previous 5-cycle increment for both fecal and mock communities after multiple comparison correction (P-value `r ifelse(min(bray_sim_to_prev_cycle_kruskal_results$bh, na.rm = T) > 0.05, invisible(">"), invisible("check data"))` 0.05). Using PERMANOVA to test for community differences based on cycle number within HiFi DNA polymerases, only Phusion had cycle dependent differences at 1000 and 5000 sub-sampling depths (P-value = `r format(filter(bray_permanova_by_taq_results, sub_sample_level == 1000, taq == "PHU")[, "bh"], digits = 1, nsmall = 1)` and `r format(filter(bray_permanova_by_taq_results, sub_sample_level == 5000, taq == "PHU")[, "bh"], digits = 1, nsmall = 1)`). For fecal samples, Phusion was one of two HiFi DNA polymerases that had enough sequences to reach a sub-sampling depth of 1000 at 15 cycles. Overall, these data suggest that there are small HiFi DNA polymerase differences in Bray-Curtis index that are dependent on both sub-sampling depth and cycle number.

### 2018-03-19 submission/manuscript.tex
update bray-curtis results section

\textbf{\emph{Minimal Bray-Curtis Differences are Detected by Cycle
Number:}} A few small differences based on sub-sampling and cycle number
were detected in bacterial communities. Within the same fecal sample and
independent of HiFi DNA polymerases, there were differences in the
community composition between 20 and 25 cycles that was dependent on
sub-sampling depth (sub-sampled to 1000 = 0.51 (0.4 - 0.79) (median
(25\% - 75\% quantile)), sub-sampled to 5000 = 0.43 (0.33 - 0.63),
sub-sampled to 10000 = 0.4 (0.24 - 0.43)) {[}Figure 3A{]}. Further,
where data was available for the mock communities, there were larger
observed differences between 20 and 25 cycles (sub-sampled to 1000 =
0.88 (0.42 - 0.91)) {[}Figure 3B{]}. Additionally, these stated
community differences disappear when comparing 25 to 30 cycles and do
not persist past 25 cycles {[}Figure 3{]}. Finally, using PERMANOVA to
test for community differences based on cycle number within HiFi DNA
polymerases, only Phusion had cycle dependent differences at 1000 and
5000 sub-sampling depths (P-value = 0.03 and 0.01, respectively).
Phusion was one of two HiFi DNA polymerases that had enough sequences to
reach a sub-sampling depth of 1000 at 15 cycles for fecal samples.

Next, we assessed whether there were any differences between 5-cycle
increments within each individual or sample replicate. For both fecal
and mock samples, we found that there was no detectable difference in
Bray-Curtis index when comparing to the previous 5-cycle increment
(P-value \textgreater{} 0.05). However, Phusion at 1000 sub-sampling
depth had a P-value = 0.02 before multiple comparison correction.
Similar to the PERMANOVA analysis, at higher sub-sampling depths these
differences in Bray-Curtis indices disappear. Overall, HiFi DNA
polymerase differences in Bray-Curtis index are dependent on both
sub-sampling depth and cycle number.

>>>>

\textbf{\emph{Minimal Bray-Curtis Differences are Detected by Cycle
Number:}} A few small differences based on sub-sampling and cycle number
were detected in overall bacterial community composition. Within the
same fecal sample and independent of HiFi DNA polymerases, there were
differences in the community composition between 20 and 25 cycles that
was dependent on sub-sampling depth (sub-sampled to 1000 = 0.51 (0.4 -
0.79) (median (IQR)), sub-sampled to 5000 = 0.43 (0.33 - 0.63),
sub-sampled to 10000 = 0.4 (0.24 - 0.43)) {[}Figure 3A{]}. Further, when
data was available for the mock communities, there were larger observed
differences between 20 and 25 cycles (sub-sampled to 1000 = 0.88 (0.42 -
0.91)) {[}Figure 3B{]}. Additionally, these stated community differences
disappear when comparing 25 to 30 cycles and do not persist past 25
cycles {[}Figure 3{]}. Although these trends are clearly noticeable, we
found that there was no detectable difference in Bray-Curtis index when
comparing to the previous 5-cycle increment for both fecal and mock
communities after multiple comparison correction (P-value \textgreater{}
0.05). Using PERMANOVA to test for community differences based on cycle
number within HiFi DNA polymerases, only Phusion had cycle dependent
differences at 1000 and 5000 sub-sampling depths (P-value = 0.03 and
0.01). For fecal samples, Phusion was one of two HiFi DNA polymerases
that had enough sequences to reach a sub-sampling depth of 1000 at 15
cycles. Overall, these data suggest that there are small HiFi DNA
polymerase differences in Bray-Curtis index that are dependent on both
sub-sampling depth and cycle number.
